Bacterial Microbiome and Obesity Meta-analysis Sequence Processing Pipeline

### 2016-02-12 code/sequenceProcessing.Rmd
sequence processing update again

```{r, engine='sh', eval=FALSE}
#!/bin/sh  
for sample in $(ls *sra)  
do  
fastq-dump $sample  
done
<br><br>
for sample2 in $(ls *fastq)  
do  
/share/scratch/schloss/mothur/mothur "#fastq.info(fastq=$sample2)"  
rm *logfile  
done
<br><br>
for TRIM in $(ls SRR*.fasta)  
do  
QFILE=\${TRIM//fasta/qual}  
/share/scratch/schloss/mothur/mothur "#trim.seqs(fasta=$TRIM, qfile=$QFILE, maxambig=0, maxhomop=8, qwindowaverage=35, qwindowsize=50, processors=8)"  
done  
rm *.fastq
```

>>>>

for sample2 in $(ls *fastq)  
do  
  /share/scratch/schloss/mothur/mothur "#fastq.info(fastq=$sample2)"  
  rm *logfile  
done
<br><br>
for TRIM in $(ls SRR*.fasta)  
do  
  QFILE=\${TRIM//fasta/qual}  
/share/scratch/schloss/mothur/mothur "#trim.seqs(fasta=$TRIM, qfile=$QFILE, maxambig=0, maxhomop=8, qwindowaverage=35, qwindowsize=50, processors=8)"  
done
